Evolution of solar wind discontinuities in the inner heliosphere

### 2024-01-29 index.qmd
update

@@

- @velliUnderstandingOriginsHeliosphere2020
- @artemyevDynamicsIntenseCurrents2018 examined the evolution of transient currents in the solar wind using a data set compiled from observations of the same solar wind ﬂow at Earth’s and Mars's orbits.
    - > we show that it consists of several processes: discontinuity thinning (decrease in thickness normalized by the ion inertial length), intensiﬁcation of currents normalized to the proton thermal current (i.e., the product of proton charge, density, and thermal velocity), and increase in the compressional component of magnetic ﬁeld variations across discontinuities.

@@

>>>>

Given timeseries $(R_a, \phi_a$, $R_b(t)$,

@@

-   @velliUnderstandingOriginsHeliosphere2020

-   @artemyevDynamicsIntenseCurrents2018 examined the evolution of transient currents in the solar wind using a data set compiled from observations of the same solar wind ﬂow at Earth’s and Mars's orbits.

    ```         
    > we show that it consists of several processes: discontinuity thinning (decrease in thickness normalized by the ion inertial length), intensiﬁcation of currents normalized to the proton thermal current (i.e., the product of proton charge, density, and thermal velocity), and increase in the compressional component of magnetic ﬁeld variations across discontinuities.
    ```

@@

## Events

2018∕10∕24 PSP Earth

```         
file:/Users/zijin/projects/psp_conjunction/files/psp_v.vap?timerange=2018-10-23+through+2018-10-25
```

PSP plasma data is very sparse (6 data point/day)

![](images/paste-13.png)

### 2019∕04∕07

``` txt
file:///Users/zijin/projects/autoplot/psp_mag_sw.vap?timerange=2019-04-06+through+2019-04-08
file:///Users/zijin/projects/autoplot/ace.vap?timerange=2019-04-08+through+2019-04-10
file:///Users/zijin/projects/autoplot/ace.vap?timerange=2019-04-11+through+2019-04-14
file:///Users/zijin/projects/autoplot/wind_plasma.vap?timerange=2019-04-08+through+2019-04-10
file:///Users/zijin/projects/autoplot/dscovr.vap?timerange=2019-04-08+through+2019-04-10
```

[ENLIL Solar Wind Prediction - Parker Solar Probe - Perihelion 02](http://helioweather.net/missions/psp/per02/)

::: {.column-page layout-nrow="1"}
{{< video http://helioweather.net/missions/psp/per02/anim/tuz-a7b1-d4t05x1-d200t1-donki_den1-psp-x15wifs3z1fo_med_201903-201904.mp4 >}}

{{< video http://helioweather.net/missions/psp/per02/anim/tuz-a7b1-d4t05x1-d200t1-donki_vel2e1-psp-x15ifs3z1fr_med_201903-201904.mp4 >}}
:::

![](images/paste-15.png)

![](images/paste-18.png)

::: {.column-page layout-nrow="1"}
![](images/paste-16.png)

![](images/paste-17.png)
:::
